---
title: "Variable importance results"
output:
  html_document:
    toc: true
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Source the script that creates result_raw and result_ranked
source("load_vimp_tables.R")
```

## Raw values

```{r raw-table}
knitr::kable(
  result_raw,
  digits = 3,
  caption = "Raw variable importance measures and estimated effects"
)
```

## Ranks

Rank 1 indicates the variable ranked as most important. For minimal depth,
smaller values receive better ranks. ATE measures are ranked by decreasing
absolute magnitude, while permutation VIMP is ranked by decreasing signed value.
Raw ATE values retain the sign of the mean predicted Y=1 risk at X=1 minus that
at X=0. Exact ties receive average ranks; missing or nonfinite values in the
comparison set stop ranking. The Effects column retains its signed coefficient
ordering and is not a common importance target across methods.

```{r ranked-table}
knitr::kable(
  result_ranked,
  digits = 1,
  caption = "Ranks of variable importance measures and estimated effects"
)
```
